---
title: "2 OLS Regression Model"
knit: (function(inputFile, encoding) { 
      out_dir <- '~/Red_Wine_Quality/';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file='2_OLS_Model.md') })
output:
  github_document:
    toc: true
    toc_depth: 2
---

# Load packages and data
```{r}
library(tidyverse)
library(stargazer)
library(lm.beta)
df <- read.csv('~/Red_Wine_Quality/winequality-red.csv')
glimpse(df)
```

# OLS Models
```{r}
model1 <- lm(quality ~ alcohol + sulphates + citric.acid + 
  volatile.acidity, data=df)
model2 <- lm(quality ~ alcohol + sulphates + citric.acid + volatile.acidity + 
  sulphates*citric.acid + citric.acid*alcohol + citric.acid*volatile.acidity
  , data=df)
stargazer(model1, model2, intercept.bottom=FALSE, type='text')
```

- Base model without interaction effects shows that citric acid does not have a statistically significant impact on quality
- Second model indicates that interactions of citric acid with sulphates and alcohol are significant
- Model performance does however not increase meaningfully
- Around 33 % of variation in quality can be described with these regressions

# Standardized Regression Coefficients
```{r}
summary(lm.beta(model2))
```

- Standardizing coefficients allows for direct comparison of effect size
- Alcohol seems to have the highest direct impact on quality

```{r}
# Export R Script
library(knitr)
knitr::purl('~/Red_Wine_Quality/9_R_Markdown/2_OLS_Model.Rmd', 
            '~/Red_Wine_Quality/9_R_Scripts/2_OLS_Model.R',
  documentation = 2, quiet = TRUE)
```
