---
title: "3_Check_OLS_Assumptions"
output:
  github_document:
    toc: true
    toc_depth: 2
---

# Load packages and data
```{r}
library(tidyverse)
library(stargazer)
library(AER)
df <- read.csv('winequality-red.csv')
glimpse(df)
```

# Recreate Model
```{r}
model2 <- lm(quality ~ alcohol + sulphates + citric.acid + volatile.acidity + 
  sulphates*citric.acid + citric.acid*alcohol + citric.acid*volatile.acidity
  , data=df)
stargazer(model2, intercept.bottom=FALSE, type="text")
```


# Check Model Assumptions
## Check Normality
```{r}
hist(df$quality)

shapiro.test(df$quality)
```

- Shapiro test: Null hypothesis has to be rejected -> Not normally distributed
- Quality does not seem to follow a normal distribution
- Visual impression does not seem too far off

### trying to restore normality
```{r}
shapiro.test(log(df$quality))
shapiro.test((df$quality)^(1/2))
shapiro.test(1/(df$quality))
```

- Transforming quality by log, square root or inverse does not restore normality

## Check Heteroskedasticity
```{r}
par(mfrow=c(2,2))
plot(model2)
bptest(model2)
```

- QQ Plot hints toward heteroskedasticity
- Breusch-Pagan test: Null hypothesis has to be rejected -> Heteroskedastic
- Use robust standard errors to not make biased interpretations of variable significance

```{r}
seBasic <- sqrt(diag(vcov(model2)))
seWhite <- sqrt(diag(vcovHC(model2, type="HC0")))

stargazer(model2, model2,  se=list(seBasic, seWhite), intercept.bottom=FALSE, type="text")
```

- Using White robust standard errors lowers significance of citric.acid interactions -> citric acid could potentially be excluded from the model, in case not much explanatory power is lost


```{r}
# Test simpler model
model3 <- lm(quality ~ alcohol + sulphates +  volatile.acidity, data=df)
stargazer(model3,intercept.bottom=FALSE, type="text")
```

- Model barely loses R², but becomes much more simple
- Additionally, all parameters are now highly significant

## Check Multicollinearity
```{r}
# Variance Inflation Factors
vif(mod=model3)
# Tolerances
1 / vif(mod=model3)
```

- Variance Inflation Factors are below 4 and Tolerances are above 0.25 -> Points toward absence of multicollinearity
