---
title: '4 OLS and kNN Regression'
output:
  github_document:
    toc: true
    toc_depth: 2
---

# Load packages and data
```{r}
library(tidymodels)
df <- read.csv('winequality-red.csv')
glimpse(df)
```

# Create train, validation and test split
```{r}
set.seed(1)
wine_split <- initial_split(df, prop = 0.7)
wine_split

wine_train <- training(wine_split)
wine_train_val <- validation_split(wine_train, prop = 0.7)
wine_test  <- testing(wine_split)
```

- Data set is split into 70% training data and 30% test data
- Out of the 70% training data, 70% are used for model training and 30 % for parameter evaluation

# Linear Regression Model
## Set model and workflow
```{r}
linear_model <- linear_reg() |> set_engine("lm")
linear_model_recipe <- recipe(quality ~ alcohol + sulphates + volatile.acidity,
  data = df)
linear_model_workflow <- workflow() |> add_model(linear_model) |> 
  add_recipe(linear_model_recipe)
linear_model_workflow
```

- Linear regression model is defined and combined into a workflow

# K-Nearest Neighbours Model
## Set model and workflow
```{r}
knn_model <- nearest_neighbor(neighbors = tune()) |> 
  set_mode("regression") |> set_engine("kknn")
knn_recipe <- recipe(quality ~ alcohol + sulphates + volatile.acidity,
  data = df) |> step_normalize(all_predictors())
knn_workflow <- workflow() |> add_model(knn_model) |> 
  add_recipe(knn_recipe)
knn_workflow
```

- K-nearest neighbor model is defined and combined into a workflow
- Variables are normalized to not bias distance calculations of the model
- The model parameter K will be tuned on the validation set

## Tune model
```{r}
tune_grid <- tibble(neighbors = 1:20*2)
knn_tune <- knn_workflow |> tune_grid(resamples = wine_train_val, 
    grid = tune_grid, metrics = metric_set(rmse, mae, rsq_trad))
knn_tune_metrics <- knn_tune |> collect_metrics()
```

- Tune grid is defined as 2-40 in steps of 2
- Grid search is performed to evaluate model performance with different hyper parameters

## Evaluation of tuning results
```{r}
knn_tune_metrics |> 
  ggplot(aes(x = neighbors, y = mean)) + 
  geom_point() + geom_line() + 
  facet_wrap(~ .metric, scales = "free_y")
knn_tune |> show_best("rmse", n = 5) 
knn_best_model <- select_best(knn_tune, metric = "rmse")
knn_workflow_final <- knn_workflow |> 
  finalize_workflow(knn_best_model)
```

- Model performance is evaluated on the mean absolute error, the root mean squared error and R²
- Best RMSE performance can be achieved at k=26
- Best tuning parameter is included into the workflow

# Compare model performances
```{r}
linear_model_last_fit <- linear_model_workflow |> 
  last_fit(wine_split, metrics = metric_set(rmse, mae, rsq_trad))
linear_model_metrics <- linear_model_last_fit |> collect_metrics()

knn_last_fit <- knn_workflow_final |> 
  last_fit(wine_split, metrics = metric_set(rmse, mae, rsq_trad))
knn_metrics <- knn_last_fit |> collect_metrics()

linear_model_metrics <- linear_model_metrics |> select(-.estimator, -.config) |> 
  mutate(model = "linear regression")
knn_metrics <- knn_metrics |> select(-.estimator, -.config) |> 
  mutate(model = "k-nearest neighbors")
linear_model_metrics |> bind_rows(knn_metrics) |> 
  pivot_wider(names_from = .metric, values_from = .estimate)
```

- Models are applied to test data and resulting performances are compared
- K-nearest neighbors is the better model
  - Lower errors of predictions
  - It can explain more variation of the dependent variable